Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-07-01 content.tex
No duplicate label 'lst:create_all_experiments', renamed one to 'lst:combine_all_experiments'

\begin{lstlisting}[
  language = R, 
  floatplacement = ht, 
  frame = single, 
  label = {lst:create_all_experiments},
  caption = {
    Create a collection of experiments, with 1
    generative model, and 39 candidate models.
  }
]
experiments <- c(
  list(generative_experiment),
  candidate_experiments
)
\end{lstlisting}

>>>>

\begin{lstlisting}[
  language = R, 
  floatplacement = ht, 
  frame = single, 
  label = {lst:combine_all_experiments},
  caption = {
    Create a collection of experiments, with 1
    generative model, and 39 candidate models.
  }
]
experiments <- c(
  list(generative_experiment),
  candidate_experiments
)
\end{lstlisting}
